First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-08-01 ms.tex
Added reference to Greig 2016

Using the first generation of instruments, several upper limits have been placed on the 21 
cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}, and 
\citet{Pober:2015} was able to place constraints on physical reionization models. 
However, much work is to be done to understand the data produced by these arrays. 
Foreground subtraction and isolation has emerged as a priority in the field. Central to most 
analysis strategies is the concept of an ``EoR window" -- the region of Fourier space where 
spectrally smooth foregrounds have been isolated from the isotropic (spherically symmetric 
in Fourier space) cosmological signal \citep{Morales:2006, Bowman:2009}. More recent 
studies have shown the existence of a foreground ``wedge", the result of instrumental mode 
mixing, throwing power from spectrally smooth foregrounds to higher Fourier modes 
\citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2012, Liu:2014a, Liu:2014b, 
Hazelton:2013, Pober:2013, Thyagarajan:2013, Vedantham:2012, Morales:2012, Datta:2010}, 
while others are investigating the spectral structure of point sources themselves \cite[e.g.][]{Offringa:2016}.
The EoR window is still expected to be preserved above the wedge, and 
several analysis pipelines are under active development \citep[e.g. B.~J.~Hazelton et al. 2016, in 
prep; D.~A.~Mitchell et al. 2016, in prep; ][]{Jacobs:2016, Trott:2016, 
Dillon:2015b, Dillon:2013, Trott:2014}.

>>>>

Using the first generation of instruments, several upper limits have been placed on the 21 
cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}.
Furthermore, \citet{Pober:2015} and \citet{Greig:2016} were able to place constraints on physical reionization models. 
However, much work is to be done to understand the data produced by these arrays. 
Foreground subtraction and isolation has emerged as a priority in the field. Central to most 
analysis strategies is the concept of an ``EoR window" -- the region of Fourier space where 
spectrally smooth foregrounds have been isolated from the isotropic (spherically symmetric 
in Fourier space) cosmological signal \citep{Morales:2006, Bowman:2009}. More recent 
studies have shown the existence of a foreground ``wedge", the result of instrumental mode 
mixing, throwing power from spectrally smooth foregrounds to higher Fourier modes 
\citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2012, Liu:2014a, Liu:2014b, 
Hazelton:2013, Pober:2013, Thyagarajan:2013, Vedantham:2012, Morales:2012, Datta:2010}, 
while others are investigating the spectral structure of point sources themselves \cite[e.g.][]{Offringa:2016}.
The EoR window is still expected to be preserved above the wedge, and 
several analysis pipelines are under active development \citep[e.g. B.~J.~Hazelton et al. 2016, in 
prep; D.~A.~Mitchell et al. 2016, in prep; ][]{Jacobs:2016, Trott:2016, 
Dillon:2015b, Dillon:2013, Trott:2014}.
